Metropolitan Areas (Deaths & Case)

### 2020-11-13 KPMG Team/Dashboard/visualization_scripts/msa_county_state_cities.Rmd
Exported Visualizations for Presentation

state_covid_sum_merge <- state_covid_sum %>% 
  rename(msa_state = "state") %>% 
  select(msa_state, date, cases_sum, deaths_sum)

@@

# Plot State Map with Metro Areas

@@

@@

@@

  ggplot(data = county_map_state) +
    geom_sf(aes(fill = cases)) + 
    scale_fill_viridis_c(option = "magma", direction = -1) + 
    labs(title = paste(state_name))

@@

# e.g. 
TX <- county_state_map("Texas")
CA <- county_state_map("California")
FL <- county_state_map("Florida")
NY <- county_state_map("New York")
IL <- county_state_map("Illinois")
GA <- county_state_map("Georgia")

@@

plot_grid(TX, CA, FL, NY, IL, GA, ncol = 2)

# msa state map 
msa_state_map <- function(msa) {

@@

#   return(df)
# }  
  # plot
  ggplot() +
    geom_sf(data = state_map, aes(fill = region_cases)) +
    geom_sf(data = msa_map_state, aes(fill = cases)) + 
    scale_fill_viridis_c(option = "magma", direction = -1) + 
    labs(title = state_map$state,
         subtitle = "Metropolitan Statistical Areas") + 
    theme_void()

@@

35614 # nyc is missing

df_ny <- msa_state_map_US("New York")

View(df_ny$msa_map_state)

msa_map %>% 
  filter(state == "New York")

plot_grid(TX, CA, FL, NY, IL, GA, ncol = 2)

@@

plot_grid(TX_msa, CA_msa, FL_msa, IL_msa, MA_msa, NJ_msa, ncol = 2)

# ggsave("metro-state.png")
```
### Metropolitan Cases

>>>>

state_covid_sum_merge <- state_sum %>% 
  rename(msa_state = "state") %>% 
  select(msa_state, date, cases_sum, deaths_sum)

@@

```{r}
# Plot State Map with Metro Areas

@@

ggplot() +
  geom_sf(data = state_map_US, aes(fill = cases)) + 
  geom_sf(data = msa_map_US, aes(fill = cases)) + 
  scale_fill_viridis_c(option = "magma", direction = -1) + 
  theme_void()

@@

ggsave("state-msa-us.png", width = 8, height = 5, dpi = 300)
```

```{r}
# \/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\\/\/\/ #
# *************** FUNCTION: PLOT DAILY COVID ONE STATE GRAPH ********************** # 
# \/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\/\\/\/\/ #

@@

  ggplot(data = county_map_state) +
    geom_sf(aes(fill = cases)) + 
    scale_fill_viridis_c(option = "magma", direction = -1) + 
    labs(title = paste(state_name)) +
    theme_void()

@@

# e.g. 
TX <- county_state_map("Texas")
CA <- county_state_map("California")
FL <- county_state_map("Florida")
MA <- county_state_map("Massachusetts")
# NY <- county_state_map("New York")
NJ <- county_state_map("New Jersey")
IL <- county_state_map("Illinois")
# GA <- county_state_map("Georgia")

@@

plot_grid(TX, CA, FL, IL, MA, NJ, ncol = 3)
```

```{r}
# msa state map 
msa_state_map <- function(msa) {

@@

#   return(df)
# }  
  # plot
  ggplot() +
    geom_sf(data = state_map, aes(fill = region_cases)) +
    geom_sf(data = msa_map_state, aes(fill = cases)) + 
    scale_fill_viridis_c(option = "magma", direction = -1) + 
    labs(title = state_map$state) +
         # subtitle = "Metropolitan Statistical Areas") + 
    theme_void()

@@

# 35614 # nyc is missing

# df_ny <- msa_state_map_US("New York")
# 
# View(df_ny$msa_map_state)
# 
# msa_map %>% 
#   filter(state == "New York")

@@

plot_grid(TX_msa, CA_msa, FL_msa, IL_msa, MA_msa, NJ_msa, ncol = 3)

# ggsave("county-state.png", width = 8, height = 5, dpi = 300)
```
### Metropolitan Cases
